---
title: "Technical Summary"
author: "Ozgur"
date: '2023-03-07'
output: 
  html_document:
    toc: no
---
<style>
.main-container {
  max-width: 940px;
  margin-left: 0;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Importing libraries
```{r libraries, results='hide'}
library(tidyverse)
library(grDevices)
library(DT)
library(lubridate)
```

## Explanation for Data Download Part

Could be found on https://github.com/ozgurseker/colorful-technical-analysis-summary


## Importing Data 
If you want to save data for future, set savedata TRUE. 
```{r dataimport}
df <- read_csv("data.csv")
savedata <- TRUE
```

## Calculate Pivot and Resistance/Supports
This calculation is based on https://www.fidelity.com/learning-center/trading-investing/technical-analysis/technical-indicator-guide/pivot-points-resistance-support

```{r srcalculation}
df <- df %>% mutate(Pivot = round((Last+High+Low)/3,2)) %>%
  mutate(Res1 = round(2*Pivot - Low, 2),
         Sup1 = round(2*Pivot - High, 2),
         Res2 = round(Pivot + Res1 - Sup1, 2),
         Sup2 = round(Pivot - Res1 + Sup1, 2),
         Res3 = round(High + 2*(Pivot - Low), 2),
         Sup3 = round(Low - 2*(High - Pivot), 2))
if(savedata){
  write.csv(df, paste0("saveddata/",today(),".csv"))
}
```

## Colorful Technical Summary

You could check the color names here. Distinct argument could be FALSE to see variations.
```{r colors1, results='hide'}
grDevices::colors(distinct = TRUE)
```

Set colors for each signal. 
```{r colors2}
signals <- c("Strong Buy", "Buy", "Neutral", "Sell", "Strong Sell")
signalColors <- c("darkgreen", "palegreen", "lavender", "tomato", "firebrick")
```

Select our columns and format their background colors 
```{r colors3}
if("ema14" %in% colnames(df)){
  dftmp <- df %>% select(Symbol, `5 Minutes`:Monthly, ema14, ma55, ma200, Sup3, Sup2, Sup1, Pivot, Res1, Res2, Res3, Last, `Chg. %`, volume, vsma5, vsma20)
  colnames(dftmp)[1:9] <- c("Symbol", "5Min","15Min", "30Min","Hourly","5Hours","Daily","Weekly","Monthly")
  dftmp <- dftmp %>% select(-`5Min`, -Monthly, -`30Min`)
  dftmp <- dftmp %>% mutate(DistEma14 = round(100*(Last - ema14)/Last,2),
                            DistMa55 = round(100*(Last - ma55)/Last,2),
                            DistMa200 = round(100*(Last - ma200)/Last,2),
                            VolDist20 = round(100*(volume - vsma20)/volume,2),
                            VolDist5 = round(100*(volume - vsma5)/volume,2)) %>% 
    mutate(across(ema14:ma200, ~ round(.x,2))) %>% select(-volume, -vsma20,-vsma5)
  datatable(dftmp) %>% formatStyle(names(dftmp), backgroundColor = styleEqual(signals, signalColors)) %>%
  formatStyle(columns = c("Res1","Res2","Res3"), target = "cell", color = "red") %>% 
  formatStyle(columns = c("Sup1","Sup2","Sup3"), target = "cell", color = "green") %>%
  formatStyle(columns = c("DistEma14", "DistMa55", "DistMa200", "VolDist20", "VolDist5"), backgroundColor = styleInterval(c(0), c("tomato", "palegreen")))
  
} else{
  dftmp <- df %>% select(Symbol, `5 Minutes`:Monthly, Sup3, Sup2, Sup1, Pivot, Res1, Res2, Res3, Last, `Chg. %`)
  colnames(dftmp)[1:9] <- c("Symbol", "5Min","15Min", "30Min","Hourly","5Hours","Daily","Weekly","Monthly")
  datatable(dftmp) %>% formatStyle(names(dftmp), backgroundColor = styleEqual(signals, signalColors)) %>%
  formatStyle(columns = c("Res1","Res2","Res3"), target = "cell", color = "red") %>% 
  formatStyle(columns = c("Sup1","Sup2","Sup3"), target = "cell", color = "green")
}


```


```{r colors4}
if("ema14" %in% colnames(df)){
  dftmp <- df %>% select(Symbol, `5 Minutes`:Monthly, ema14, ma55, ma200, Sup3, Sup2, Sup1, Pivot, Res1, Res2, Res3, Last, `Chg. %`, volume, vsma5, vsma20)
  colnames(dftmp)[1:9] <- c("Symbol", "5Min","15Min", "30Min","Hourly","5Hours","Daily","Weekly","Monthly")
  dftmp <- dftmp %>% select(-`5Min`, -Monthly, -`30Min`)
  dftmp <- dftmp %>% mutate(DistEma14 = round(100*(Last - ema14)/Last,2),
                            DistMa55 = round(100*(Last - ma55)/Last,2),
                            DistMa200 = round(100*(Last - ma200)/Last,2),
                            VolDist20 = round(100*(volume - vsma20)/volume,2),
                            VolDist5 = round(100*(volume - vsma5)/volume,2)) %>% 
    mutate(across(ema14:ma200, ~ round(.x,2))) %>% select(-volume, -vsma20,-vsma5)
  datatable(dftmp %>% filter(VolDist5>0, VolDist20>0)) %>% formatStyle(names(dftmp), backgroundColor = styleEqual(signals, signalColors)) %>%
  formatStyle(columns = c("Res1","Res2","Res3"), target = "cell", color = "red") %>% 
  formatStyle(columns = c("Sup1","Sup2","Sup3"), target = "cell", color = "green") %>%
  formatStyle(columns = c("DistEma14", "DistMa55", "DistMa200", "VolDist20", "VolDist5"), backgroundColor = styleInterval(c(0), c("tomato", "palegreen")))
  
}

```
